Standalone Tactics using OpenTheory

### 2012-01-26 paper.tex
minor tweaks on intro

It makes sense to speak of similar functionality in different systems not just because they use roughly the same logic, but also because there is a shared base of concepts: booleans, inductive datatypes, recursive functions, natural numbers, lists, sets, etc.  
The \OpenTheory standard library~\cite{DBLP:conf/nfm/Hurd11} formalises this shared base, using \OpenTheory~\cite{hurd2009}, a format designed for storing and sharing higher-order logic theories.
We use \OpenTheory to communicate to tactics (sending goals and receiving proofs), and thereby obtain
\begin{enumerate}
\item
A standard format (article files) for goals and proofs, and
\item
An extensible way to fix the meaning of constants and type definitions.
\end{enumerate}

Examples of duplicate effort include the integration of external tools into HOL-based provers.
For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
Sledgehammer~\cite{DBLP:journals/japll/MengP09,Paulson_threeyears,DBLP:conf/frocos/BlanchetteBN11} is only available for Isabelle/HOL, but would be useful if available for other provers.

>>>>

It makes sense to speak of similar functionality in different systems not just because they use roughly the same logic, but also because there is a shared base of concepts: booleans, inductive datatypes, recursive functions, natural numbers, lists, sets, etc.  
The \OpenTheory standard library~\cite{DBLP:conf/nfm/Hurd11} formalises this shared base, using \OpenTheory~\cite{hurd2009}, a format designed for storing and sharing higher-order logic theories.
We use \OpenTheory to communicate with tactics (sending goals and receiving proofs), and thereby obtain
\begin{enumerate}
\item
A standard format (\OpenTheory article files) for goals and proofs, and
\item
An extensible way to fix the meaning of constants and type definitions.
\end{enumerate}

Examples of duplicated effort on tactics include the integration of external tools into HOL-based provers.
For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
Sledgehammer~\cite{DBLP:journals/japll/MengP09,Paulson_threeyears,DBLP:conf/frocos/BlanchetteBN11} is only available for Isabelle/HOL, but would be useful if available for other provers.
